Equalizer 2.0\\Convergence of a Parallel Rendering Framework

### 2017-04-03 paperIEEE.tex
Polishing
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@31 db7c848b-7755-4df2-b763-8796797afa52

This section presents new experiments, complementing the results of previous
publications~\cite{EP:07, EMP:09, MEP:10, EEP:11, EBAHMP:12, HBBES:13, deflect,
  SPEP:16}. The first part analyses data distribution performance, in particular
how the various optimizations in Collage effect complex operations in realistic
scenarios. The second part summarizes rendering performance over all
decomposition modes with a few representative workloads.

@@

@@

@@

A critical piece for data distribution performance are the characteristics of
the data compression algorithms. This microbenchmark compresses a set of binary
files to precalculate the speed and compression ratio of the various
engines. \fig{fCompressor} shows the compression and decompression speed in
gigabyte per second as well as the size of the compressed data. The different
ZSTD$x$ engines use the ZStandard compression library at level $x$.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/stefan}}]{Stefan Eilemann}
Stefan is the technical manager of the Visualization Team in the Blue Brain
Project. His work involves working towards large-scale visualization for
Exascale simulations; interactive integration of simulation, analysis and
visualization as well as flexible frameworks for data sharing and dynamic
allocation of heterogenous resources. He is the CEO and founder of Eyescale and
also the lead developer of the Equalizer parallel rendering framework. He has
worked in SGI's Advanced Graphics Division as the technical lead of OpenGL
Multipipe SDK - a toolkit for scalable, parallel visualization software on
shared memory supercomputers. He received his masters degree in Computer Science
from EPFL in 2015, and his Engineering Diploma in Computer Science in 1998.
\end{IEEEbiography}

>>>>

This section presents new experiments, complementing the results of previous
publications~\cite{EP:07, EMP:09, MEP:10, EEP:11, EBAHMP:12, HBBES:13, deflect,
  SPEP:16}. The first part summarizes rendering performance over all
decomposition modes with a few representative workloads. The second part
analyses data distribution performance, in particular how the various
optimizations in Collage effect complex operations in realistic scenarios.

@@

The data distribution benchmarks have been performed on a cluster using
dual processor Intel Xeon X5690 CPUs (3.47GHz), 24 GB main memory, 10GBit/s
Ethernet and QDR Infiniband. Intel ICC 2017 has been used with CMake 3.2 release
mode settings to compile the software stack.

@@

\begin{figure}[ht]\center
  \includegraphics[width=.49\columnwidth]{images/david2mm}
  \caption{\label{fDavid2mm}David statue at 2mm resolution (145MB)}
\end{figure}

The ply file is converted into a kd-Tree for fast view frustum culling and
rendering, and the resulting data structure is serialized in binary form for
data transmission.

@@

A critical piece for data distribution performance are the characteristics of
the data compression algorithms. This microbenchmark compresses a set of binary
files to precalculate the speed and compression ratio of the various
engines. \fig{fCompressor} shows the compression and decompression speed in
gigabyte per second as well as the size of the compressed data. The different
ZSTD$x$ engines use the ZStandard compression library at level $x$. The
measurements were performed on a single, isolated node.

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{images/stefan}}]{Stefan Eilemann}
Stefan is the technical manager of the Visualization Team in the Blue Brain
Project. His work involves working towards large-scale visualization for
Exascale simulations; interactive integration of simulation, analysis and
visualization as well as flexible frameworks for data sharing and dynamic
allocation of heterogenous resources. He is the CEO and founder of Eyescale and
also the lead developer of the Equalizer parallel rendering framework. He has
worked in SGI's Advanced Graphics Division as the technical lead of OpenGL
Multipipe SDK - a toolkit for scalable, parallel visualization software on
shared memory supercomputers. He received his masters degree in Computer Science
from EPFL in 2015, and his Engineering Diploma in Computer Science in 1998. He
is currently working towards a PhD in Computer Science at the Visualization and
Multimedia Lab at the University of Zurich.
\end{IEEEbiography}
